Out-of-Sample Comparisons of Overfit Models

### 2013-12-20 paper.tex
Fix typo in extended example

Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
\bar{D}_T$.  We can write this as
\begin{align*}
  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}'
  \hat{\theta}_{2R} - \hat{\theta}_{2T}' \hat{\theta}_{2T} \\ &=
  \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \eb_T
\end{align*}
with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
Standard results for the moments of quadratic forms and of the
Inverse-Wishart distribution \citep{Haf:79} imply that
\begin{equation*}
  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
\end{equation*}
and
\begin{align*}
  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
  O(P/T)^2.
\end{align*}
So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$ only
if $P^3/T^2 \to 0$, which is slightly weaker than the general
requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the \oos\ average
still obeys the \mds\ \clt, but it is not centered correctly at $\E_T
\oosB$.

>>>>

Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
\bar{D}_T$.  We can write this as
\begin{align*}
  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}'
  \hat{\theta}_{2R} - \hat{\theta}_{2T}' \hat{\theta}_{2T} \\ &=
  \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \eb_T
\end{align*}
with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
Standard results for the moments of quadratic forms and of the
Inverse-Wishart distribution \citep{Haf:79} imply that
\begin{equation*}
  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
\end{equation*}
and
\begin{align*}
  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
  O(P/T)^2.
\end{align*}
So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
if $P^3/T^2 \to 0$, which is slightly weaker than the general
requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the \oos\ average
still obeys the \mds\ \clt, but it is not centered correctly at $\E_T
\oosB$.
